Use GOstats to test for over-represented GO terms
========================================================

```{r}
library(GOstats)
library(GSEABase)
library(GOstatsPlus)
```

### Create gene set
Create a GOstat gene set collection (gsc) object based on a text file having
the format gene_id\tGO_id\tDescription\n (e.g .annot file export from Blast2GO)

This is a bit time consuming, so do save the R object for later reuse

```{r}
if(file.exists("organism_gsc.rda")){
  load(file="organism_gsc.rda")
}else{
  fn_annot <- system.file("extdata", "example_GO_b2g.annot", package="GOstatPlus")
  GO_gsc = b2g_to_gsc(file=fn_annot,organism="myOrganism")
  save(GO_gsc,file="organism_gsc.rda")
}

```

### Perform test
Genes of interest vs all genes that have any GO annotation (default)
Perform tests for over-represented (default) biological process, molecular function and cellular component terms:

```{r}
gene_IDs_of_interest = head(unique(unlist(geneIds(GO_gsc))),500)

GO_BP<-test_GO(gene_IDs_of_interest, ontology="BP", gsc=GO_gsc, pval = 0.01)
GO_MF<-test_GO(gene_IDs_of_interest, ontology="MF", gsc=GO_gsc, pval = 0.01)
GO_CC<-test_GO(gene_IDs_of_interest, ontology="CC", gsc=GO_gsc, pval = 0.01)
```

### View results
```{r}
head(summary(GO_BP))
head(summary(GO_MF))
head(summary(GO_CC))
```

###Export list of significant term, e.g. for import/visualization in REViGO (http://revigo.irb.hr)
```{r}
go_terms = unlist(lapply(c(GO_BP,GO_MF,GO_CC),function(d){significant_terms(d,cutoff=0.01)}))
write.table(go_terms,file="go_terms.significant.txt",quote=FALSE)
```
